What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
more content to undocumented section

To better investigate the extent of this problem we classified each stack trace according to the type of the
root exception. Table~\ref{typeroottab} presents the types of root causes of all stack traces reported on 
the Android repositories. As we can see from Table ~ref{typeroottab},  most of the exceptions signaled by third-party code
 (e.g., Android and libs) were runtime exceptions. After filtering all the exceptions implicitly signaled by 
JVM (due to programming mistakes) and inspecting the signaler methods of such exceptions (i.e.,  direct an inderect 
instances of java.lang.RuntimeException). We could observe observe that only 1 method out of 118 inspected signalers
 (i.e., 0,8%) documented the explicitly thrown runtime exceptions in a Javadoc comment, and none of the analized 
included the exception  as part of the exception interface of the method (i.e., using throws clause on method signature). 
This result is aligned with the results of other  study conducted by from 
Sacramento et al ~\cite{sacramento2006unchecked} which observed that the
runtime exceptions in .Net programs are most often not documented.

>>>>

To better investigate the extent of this problem we classified each stack trace according to the type of the
root exception. Table~\ref{typeroottab} presents the types of root causes of all stack traces reported on 
the Android repositories. As we can see from Table ~ref{typeroottab},  most of the exceptions signaled by third-party code
 (e.g., Android and libs) were runtime exceptions. After filtering all the exceptions implicitly signaled by 
JVM (due to programming mistakes) and inspecting the signaler methods of such exceptions (i.e.,  direct an inderect 
instances of java.lang.RuntimeException). We could observe observe that only 1 method out of 118 inspected signalers
 (i.e., 0,8%) documented the explicitly thrown runtime exception in a Javadoc comment; and none of these methods
included the runtime exception  (reported on the stack) as part of the exception interface of the method (i.e., using 
throws clause on method signature). This result is aligned with the results of other  study conducted by from 
Sacramento et al ~\cite{sacramento2006unchecked} which observed that the
runtime exceptions in .Net programs are most often not documented.
